Transforming Trash as an Artistic Act

### 2015-12-16 main.tex
Thesis format edits
Former-commit-id: d1dea8cb723a1b15083a10b05c3c9849cab174b9

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,left=40mm,right=25mm,top=25mm,bottom=25mm]{geometry}
\usepackage{epigraph}
\usepackage{graphicx}
%\graphicspath{ {graphics/} }
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage[titletoc]{appendix}
\usepackage[colorinlistoftodos]{todonotes}

%\usepackage{chngcntr}
%\counterwithout{figure}{chapter}

%\usepackage{setspace}
%\doublespacing

\usepackage[doublespacing]{setspace}

@@

\hypersetup{
    pdftitle			= {Thesis Draft},
    pdfauthor			= {Mustafa ilhan},
    pdfsubject			= {Trash, Art},
    pdfkeywords			= {mfa thesis, trash, art},
    colorlinks			= false,
    pdfborder			= {0 0 0},
    pdfpagemode			= UseOutlines
}

@@

\addto\captionsenglish{%
  \renewcommand{\contentsname}{\MakeUppercase{Table of Contents}}%
  \renewcommand{\listtablename}{\MakeUppercase{List of Tables}}%
  \renewcommand{\listfigurename}{\MakeUppercase{List of Figures}}%
  \renewcommand{\bibname}{\MakeUppercase{Bibliography}}%
}

@@

\begin{document}
\selectlanguage{english}

\begin{titlepage}
    \begin{center}

@@

        \vfill
        Department of\\
        Communication and Design\\
        İhsan Doğramacı Bilkent University\\
        Ankara\\
        \today
        \vspace{25mm}

    \end{center}
\end{titlepage}

\begin{titlepage}
    \begin{center}

        \vspace*{25mm}
        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
        \vspace*{4\baselineskip}
        Graduate School of Economics and Social Sciences\\
        of\\
		İhsan Doğramacı Bilkent University\\
		\vspace*{3\baselineskip}
        by\\
       	\vspace*{3\baselineskip}
        MUSTAFA İLHAN\\
        \vspace*{4\baselineskip}
        In Partial Fulfilment of the Requirements for the Degree of\\
		MASTER FINE OF ARTS\\
        \vspace{2\baselineskip}
        in\\
        \vspace{2\baselineskip}
        THE DEPARTMENT OF\\
        COMMUNICATION AND DESIGN\\
       	İHSAN DOĞRAMACI BİLKENT UNIVERSITY\\
        ANKARA\\
        \vspace{\baselineskip}
        January 2016

    \end{center}
\end{titlepage}

@@

%****************************************
% ENGLISH
\begin{abstract}
Usage of non-art objects in the artworks can be traced back to the beginning of 20th century. This approach has broken the existing rules and extended the language of art in an unprecedented way. After that point, trash has found a place in the work of artists \comment{(and their expression)}.

@@

\vfill\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Trash as an Art Material.
\end{abstract}
%........................................

\selectlanguage{turkish}
%****************************************
% TURKISH
\begin{abstract}
\comment{Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir. Ya da en azından proje kapsamında üretilen işin. Ya da bu bağlamda ele alınabileceği iddia edilmektedir.}

@@

\vfill\noindent\textbf{Anahtar Kelimeler:} Çöpün Dönüştürülmesi, Sanatta Çöp.
\end{abstract}
%........................................
\selectlanguage{english}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\tableofcontents

\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
%{%
%\let\oldnumberline\numberline%
%\renewcommand{\numberline}{\figurename~\oldnumberline}%
%\listoffigures%
%}

%\listoftables
\listoftodos

\pagenumbering{arabic}
\include{chapter1_reduced}
\include{chapter2_reduced}
\include{chapter3_reduced}
\include{chapter4_reduced}
\include{chapter5}

\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{apacite}
\bibliography{literature}
\begin{appendices}
\include{appendix_glossary}
\end{appendices}

>>>>

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,left=40mm,right=25mm,top=25mm,bottom=25mm]{geometry}
\usepackage{epigraph}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage[titletoc]{appendix}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{afterpage}
\usepackage[doublespacing]{setspace}
\usepackage{tocloft}

\usepackage{chngcntr}
\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}

@@

\hypersetup{
    pdftitle			= {MFA Thesis},
    pdfauthor			= {Mustafa ilhan},
    pdfsubject			= {Trash, Art},
    pdfkeywords			= {mfa thesis, trash, art},
    colorlinks			= false,
    pdfborder			= {0 0 0},
    pdfpagemode			= UseOutlines
}

@@

% RENAMING CHAPTER TITLES
\addto\captionsenglish{%
  \renewcommand{\contentsname}{\MakeUppercase{Table of Contents}}%
  \renewcommand{\listtablename}{\MakeUppercase{List of Tables}}%
  \renewcommand{\listfigurename}{\MakeUppercase{List of Figures}}%
  \renewcommand{\bibname}{\MakeUppercase{Bibliography}}%
}

@@

%****************************************
% BEGIN
\begin{document}
\pagenumbering{gobble}
\selectlanguage{english}

%****************************************
% COVER
\begin{titlepage}
    \begin{center}

@@

        \vfill
        Department of\\
        Communication and Design\\
        İhsan Doğramacı Bilkent University\\
        Ankara\\
        January 2016
        \vspace{25mm}

    \end{center}
\end{titlepage}
%........................................

%****************************************
% BLANK PAGE
\clearpage
\afterpage{\null\newpage}
\clearpage
%........................................

%****************************************
% DEDICATION
\newenvironment{dedication}
  {\clearpage           % we want a new page
   \thispagestyle{empty}% no header and footer
   \vspace*{2in}		% some space at the top 
   \centering
  }
  {\par					% end the paragraph
   \vfill
   \clearpage           % finish off the page
  }

\begin{dedication}
To my family and for those who embrace trash
\end{dedication}
%........................................

@@

%****************************************
% TITLE PAGE
\clearpage
\thispagestyle{empty}
\singlespacing
	\begin{center}

        \vspace*{25mm}
        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
        \vspace*{4\baselineskip}
        Graduate School of Economics and Social Sciences\\
        of\\
		İhsan Doğramacı Bilkent University\\
		\vspace*{3\baselineskip}
        by\\
       	\vspace*{3\baselineskip}
        MUSTAFA İLHAN\\
        \vspace*{4\baselineskip}
        In Partial Fulfilment of the Requirements for the Degree of\\
		MASTER FINE OF ARTS\\
        \vspace{2\baselineskip}
        in\\
        \vspace{2\baselineskip}
        THE DEPARTMENT OF\\
        COMMUNICATION AND DESIGN\\
       	İHSAN DOĞRAMACI BİLKENT UNIVERSITY\\
        ANKARA\\
        \vspace{\baselineskip}
        January 2016
	\end{center}
\clearpage
%........................................

%****************************************
% APPROVAL PAGE
\clearpage
\thispagestyle{empty}
\singlespacing
\noindent I certify that I have read this thesis and have found that it is fully adequate, in scope and in quality, as a thesis for the degree of Master of Fine Arts in Media and Design.\\

\noindent---------------------------------\\
Assist. Prof. Dr. Ersan Ocak\\
Supervisor\\

\noindent I certify that I have read this thesis and have found that it is fully adequate, in scope and in quality, as a thesis for the degree of Master of Fine Arts in Media and Design.\\

\noindent---------------------------------\\
Prof. Dr. Mehmet Yılmaz\\
Examining Commitee Member\\

\noindent I certify that I have read this thesis and have found that it is fully adequate, in scope and in quality, as a thesis for the degree of Master of Fine Arts in Media and Design.\\

\noindent---------------------------------\\
Instructor Ekin Kılıç\\
Examining Commitee Member\\

\noindent Approval of the Graduate School of Economics and Social Sciences\\

\noindent---------------------------------\\
Prof. Dr. Halime Demirkan\\
Director\\

\clearpage
%........................................

%****************************************
% ENGLISH ABSTRACT
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{ABSTRACT}
\doublespacing
\begin{center}
	\vspace*{25mm}
	\MakeUppercase{Abstract}\\
    \vspace{\baselineskip}
    TRANSFORMING TRASH AS AN ARTISTIC ACT\\
    İlhan, Mustafa\\
    M.F.A., Department of Communication and Design\\
    Supervisor: Assist. Prof. Dr. Ersan Ocak\\
    \vspace{\baselineskip}
    January 2016
\end{center}
\singlespacing
\par Usage of non-art objects in the artworks can be traced back to the beginning of 20th century. This approach has broken the existing rules and extended the language of art in an unprecedented way. After that point, trash has found a place in the work of artists \comment{(and their expression)}.

@@

\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Trash as an Art Material.
\clearpage
%........................................

%****************************************
% TURKISH ABSTRACT
\thispagestyle{plain}
\selectlanguage{turkish}
\addcontentsline{toc}{chapter}{ÖZET}
\doublespacing
\begin{center}
	\vspace*{25mm}
	\MakeUppercase{Özet}\\
    \vspace{\baselineskip}
    \MakeUppercase{Sanatsal Bir Eylem Olarak Çöpü Dönüştürme}\\
    İlhan, Mustafa\\
    Yüksek Lisans, İletişim ve Tasarım Bölümü\\
    Tez Yöneticisi: Yrd. Doç. Dr. Ersan Ocak\\
    \vspace{\baselineskip}
    Ocak 2016
\end{center}
\singlespacing
\par \comment{Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir. Ya da en azından proje kapsamında üretilen işin. Ya da bu bağlamda ele alınabileceği iddia edilmektedir.}

@@

\noindent\textbf{Anahtar Kelimeler:} Çöpün Dönüştürülmesi, Sanatta Çöp.
\clearpage
%........................................

\selectlanguage{english}

%****************************************
% ACKNOWLEDGMENTS
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\doublespacing
\begin{center}
	\vspace*{25mm}
	\MakeUppercase{ACKNOWLEDGMENTS}\\
    \vspace{3\baselineskip}
\end{center}
\par First and foremost, I would like to thank to my thesis supervisor Ersan Ocak for his continuous patience, support, encouragement and immense knowledge that he shared with me through the entire process. I cannot imagine having a better advisor for both this written thesis and the project I conducted. I also would like to thank the rest of my thesis committee; Mehmet Yılmaz and Ekin Kılıç for their motivation and insightful comments.
\clearpage
%........................................

%****************************************
% TABLE OF CONTENTS
\addcontentsline{toc}{chapter}{Table of Contents}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}} % dots for chapters
\renewcommand{\cfttoctitlefont}{\normalfont\MakeUppercase\hfil}
\renewcommand\cftchapfont{\mdseries}
\renewcommand\cftchappagefont{\mdseries}
\renewcommand{\cftchappresnum}{Chapter\space}
\renewcommand{\cftchapaftersnum}{:}

\setlength{\cftbeforetoctitleskip}{25mm}
\setlength{\cftaftertoctitleskip}{3\baselineskip}
\setlength{\cftchapnumwidth}{5em}
%\addtolength{\cftchapnumwidth}{\cftchappresnum\cftchapaftersnum}

\begin{singlespace}
\tableofcontents
\end{singlespace}
\clearpage
%........................................

%****************************************
% LIST OF FIGURES
\addcontentsline{toc}{chapter}{List of Figures}

\renewcommand{\cftloftitlefont}{\normalfont\MakeUppercase\hfil}
\renewcommand{\cftfigaftersnum}{.}

\setlength{\cftbeforeloftitleskip}{25mm}
\setlength{\cftafterloftitleskip}{3\baselineskip}

\begin{singlespace}
\listoffigures
\end{singlespace}
\clearpage
%{%
%\let\oldnumberline\numberline%
%\renewcommand{\numberline}{\figurename~\oldnumberline}%
%\listoffigures%
%}
%........................................

%****************************************
% LIST OF FIGURES
%\addcontentsline{toc}{chapter}{List of Tables}
%\listoftables
%........................................

%\listoftodos

\pagenumbering{arabic}

%****************************************
% CHAPTERS
\include{chapter1_reduced}
\include{chapter2_reduced}
\include{chapter3_reduced}
\include{chapter4_reduced}
\include{chapter5}
%........................................

%****************************************
% BIBLIOGRAPHY
\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{apacite}
\begin{singlespace}
\setlength{\bibsep}{2\itemsep}
\bibliography{literature}
\end{singlespace}
\clearpage
%........................................

%****************************************
% APENDICES
\begin{appendices}
\include{appendix_glossary}
\end{appendices}
%........................................
